\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

In the context of public service modernization and improving the relationship between administration and citizens, this final year project focuses on developing a web application for managing municipal appointments for the commune of Azrou.

The main objective of this study is to design and develop an IT solution that allows citizens to book appointments online with various municipal services, while providing administrators with efficient management tools to optimize service organization.

The adopted methodology is based on an agile approach, starting with a thorough analysis of user needs (citizens and municipal staff) through interviews and observations. This analysis phase identified the key functionalities required and the technical constraints to be respected.

The proposed architecture follows the MVC (Model-View-Controller) pattern with a clear separation between the frontend (React.js) and backend (Node.js with Express). The MongoDB database ensures data persistence, while the responsive user interface guarantees optimal accessibility across all device types.

The main features developed include:
\begin{itemize}
    \item An online appointment booking system
    \item An administrative interface for service and staff management
    \item An email notification system
    \item An analytical dashboard for activity monitoring
    \item A community problem reporting module
\end{itemize}

The tests performed confirm the robustness and usability of the developed solution. The application meets the defined functional and non-functional requirements, thus contributing to improving the quality of municipal services and citizen satisfaction.

\textbf{Keywords:} E-government, Appointment management, Municipal services, Web application, React.js, Node.js, MongoDB, Azrou commune.
